---
output: github_document
editor_options: 
  markdown: 
    wrap: 72
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
------------------------------------------------------------------------

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://lifecycle.r-lib.org/articles/stages.html)
<!-- badges: end -->

## Overview

This data project contains the S7 properties, generic functions and methods used in the 
the management and maintenance of this project.

## Installation

The latest zipped package directory can be found on the network.

Once downloaded onto your machine unzip this folder, add the project as
a new project in RStudio and then install the required R packages from
CRAN by running the following commands.

```{r eval=FALSE}
install.packages("renv")
renv::activate()
renv::restore()
```

Once these additional packages have been installed, run **Build-Install
and Restart** in RStudio to build and install the package on your machine.

The package documentation can be viewed by opening the **index.html**
file, found in the docs folder, in your web browser.

## Usage

The documentation is split up into five main sections

The **information** section contains information documents relating to the project

The **lookup and functions** section contains the functions used in the R package. 
These functions are found in the R folder of the project. The inst folder contains the 
file templates and scripts used to manage and maintain the data project.

The **tasks** and **products** sections list the ongoing and completed tasks
and questions, as well as the package products for each data project version.

## Publication

This data project has been submitted to a public [dp repository](https://github.com/gcfrench/dp) on GitHub.
